Introduction

### 2024-10-12 Manuscript/manuscript.qmd
cv additions and re-render
few new references, and a re-render with the intro figure.

{{< include pre_sections/pre_pdf.qmd >}}

@@

::: {.content-visible when-format="docx"}
{{< include pre_sections/pre_docx.qmd >}}
:::

@@

Varied training has been shown to influence learning in a wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], anagram completion [@goodeSuperiorityVariableRepeated2008], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015],  the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023] ,  simple motor learning [@braunMotorTaskVariation2009; @kerrSpecificVariedPractice1978; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training  [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and  complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022]. See @czyzVariabilityPracticeInformation2021 or @ravivHowVariabilityShapes2022 for more detailed reviews.

@@

One of the earliest and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978. Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task. The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet. Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial. 12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants. Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage. In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children. This result provides particularly strong evidence for the benefits of varied practice, as the varied group outperformed the constant group even when tested at the "home-turf" distance that the constant group had exclusively practiced. A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a]. One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group. Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths. However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperforms the constant group even from the constants group's home turf has not been consistently replicated. One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet). This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups. However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).

@@

pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
  ggh4x,htmltools,future,furrr,ez)
#options(brms.backend="cmdstanr",mc.cores=4)
#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
walk(c("brms","dplyr","bayestestR","here","rstanarm"), conflict_prefer_all, quiet = TRUE)
walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
#conflicts_prefer(tidybayes::rstudent_t)

@@

@@

>>>>

{{< include pre_sections/pre_pdf_full.qmd >}}
{{< include pre_sections/acknowledgements.qmd >}}
{{< include pre_sections/abstract.qmd >}}

@@

::: {.content-visible when-format="docx"}
{{< include pre_sections/pre_docx.qmd >}}
{{< include pre_sections/acknowledgements.qmd >}}
{{< include pre_sections/abstract.qmd >}}
:::

@@

Varied training has been shown to influence learning in a wide array of different tasks and domains, including categorization [@hahnEffectsCategoryDiversity2005; @maddoxStimulusRangeDiscontinuity2011; @posnerGenesisAbstractIdeas1968; @nosofskyModelguidedSearchOptimal2019; @morgensternOneshotCategorizationNovel2019; @plebanekEffectsFrequencyVariability2021], language learning [@jonesDensityDistinctivenessEarly2020; @perryLearnLocallyThink2010; @twomeyAllRightNoises2018; @wonnacottInputEffectsAcquisition2012; @brekelmansDoesHighVariability2022], pattern and anagram completion tasks [@goodeSuperiorityVariableRepeated2008; @zhangHighVariabilityLearning2024], perceptual learning [@manentiVariabilityTrainingUnlocks2023; @lovibondStimulusDiscriminabilityInduction2020; @robsonSpecificVariedPractice2022a; @zamanPerceptualVariabilityImplications2021], trajectory extrapolation [@fulvioTaskSpecificResponseStrategy2014], cognitive control tasks [@sabahWhenLessMore2019; @moshon-cohenStimulusVariabilityImproves2024], associative learning [@leeEvidentialDiversityIncreases2019; @reichmannVariabilityAbstractionEvaluative2023; @fanStimulusDiversityIncreases2022; @pradaExperiencedCategoryVariability2020; @liveseyRevisitingPeakShift2019; @ramAnticipatedVariabilityIncreases2024], visual search [@georgeStimulusVariabilityTask2021; @gonzalezDiversityTrainingEnhances2011; @kelleyLearningAttendEffects2009], voice identity learning [@lavanEffectsHighVariability2019], face recognition [@honigPerceptualSimilarityModulates2022; @burtonIdentityVariationRepresentations2016; @menonVariationPhotosSame2015], the perception of social group heterogeneity [@linvilleExemplarAbstractionModels1993; @konovalovaInformationSamplingExplanation2020; @parkPerceptionVariabilityCategory1987; @gershmanStructureLearningPrinciples2023], simple motor learning [@braunMotorTaskVariation2009; @velazquez-vargasRoleTrainingVariability2024; @rollerVariablePracticeLenses2001; @willeyLimitedGeneralizationVaried2018], sports training [@greenPracticeVariabilityTransfer1995a; @northEffectConsistentVaried2019; @breslinConstantVariablePractice2012], and complex skill learning [@seowTransferEffectsVaried2019; @huetEducationAttentionExplanation2011; @hacquesVisualControlClimbing2022]. See @czyzVariabilityPracticeInformation2021 and @ravivHowVariabilityShapes2022 for more detailed reviews.

@@

One of the earliest and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978. Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task. The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet (see @fig-ex-design1). Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial. 12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants. Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage. In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children. This result provides particularly strong evidence for the benefits of varied practice, as the varied group outperformed the constant group even when tested at the "home-turf" distance that the constant group had exclusively practiced. A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a]. One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group. Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths. However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperforms the constant group even from the constants group's home turf has not been consistently replicated. One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet). This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups. However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).

```{r}
#| label: fig-ex-design1
#| fig-width: 10
#| fig-height: 6
#| fig-cap: "A schematic representation of the @kerrSpecificVariedPractice1978 study design. The varied group trained from two distances (2 and 4 feet), while the constant group trained from a single distance (3 feet). Both groups were tested from a distance of 3 feet. The varied group outperformed the constant group at testing, despite the constant group having exclusively practiced from the testing distance."
#| cache: false
pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
  ggh4x,htmltools,future,furrr,ez)

create_data <- function(varied_train, constant_train, both_test) {
  varied_labels <- "Varied-Train"
  constant_labels <- "Constant-Train"
  test_labels <- "Testing"

  data <- data.frame(
    x = c(varied_train, constant_train, both_test),
    y = c(rep(0.55, length(varied_train)), rep(0.75, length(constant_train)), rep(0.4, length(both_test))),
    label = c(rep(varied_labels, length(varied_train)),
              rep(constant_labels, length(constant_train)),
              rep(test_labels, length(both_test))),
    color = c(rep("#00A08A", length(varied_train)), rep("#FF0000", length(constant_train)), rep("#ECCBAE", length(both_test)))
  )

  data
}

create_segments <- function(data) {
  min_x <- min(data$x)
  max_x <- max(data$x)
  segments <- data.frame(
    x = c(min_x - 0.5, min_x - 0.5, min_x - 0.5),
    xend = c(max_x + 0.5, max_x + 0.5, max_x + 0.5),
    y = c(0.55, 0.75, 0.4),
    yend = c(0.55, 0.75, 0.4)
  )
  segments
}

create_plot <- function(varied_train, constant_train, both_test) {
  data <- create_data(varied_train, constant_train, both_test)
  segments <- create_segments(data)

  # Variables for Training segment position
  train_x <- min(data$x) - .5
  train_y_start <- 0.5
  train_y_end <- 0.8
  train_text_y <- 0.75

  # Variables for Testing segment position
  test_x <- min(data$x) - .5
  test_y_start <- 0.35
  test_y_end <- 0.45
  test_text_y <- 0.48

  ggplot() +
    geom_segment(data = segments, aes(x = x, xend = xend, y = y, yend = yend),
                 linewidth = 1.2, color = "gray40") +
    geom_point(data = data, aes(x = x, y = y, color = color), size = 12) +
    geom_text(data = data, aes(x = x, y = y, label = label),
              color = "black", size = 4.5, vjust = -1.8, hjust = 0.5, fontface = "italic") +
    geom_segment(aes(x = train_x - 0.3, xend = train_x - 0.3, y = train_y_start, yend = train_y_end), color = "black", linewidth = 1.2) +
    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_end, yend = train_y_end), color = "black", linewidth = 1.2) +
    geom_segment(aes(x = train_x - 0.5, xend = train_x, y = train_y_start, yend = train_y_start), color = "black", linewidth = 1.2) +
    geom_text(aes(x = train_x - .6, y = train_text_y, label = "Training"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4.5, fontface = "bold") +
    geom_segment(aes(x = test_x - 0.3, xend = test_x - 0.3, y = test_y_start, yend = test_y_end), color = "black", linewidth = 1.2) +
    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_end, yend = test_y_end), color = "black", linewidth = 1.2) +
    geom_segment(aes(x = test_x - 0.5, xend = test_x, y = test_y_start, yend = test_y_start), color = "black", linewidth = 1.2) +
    geom_text(aes(x = test_x - .6, y = test_text_y, label = "Testing"), angle = 90, vjust = 0.5, hjust = 1.5, size = 4.5, fontface = "bold") +
    scale_color_manual(values = c("#00A08A","#ECCBAE", "#FF0000")) +
    xlim(min(data$x) - 2, max(data$x) + 1) +
    ylim(0.3, 1) +
    theme_void() +
    theme(legend.position = "none",
          plot.margin = margin(10, 20, 10, 20),
          plot.background = element_rect(fill = "white", color = NA),
          panel.background = element_rect(fill = "white", color = NA))
}

kerr_booth_1978 <- create_plot(varied_train = c(2, 4), constant_train = c(3), both_test = c(3))
kerr_booth_1978
```

@@

#options(brms.backend="cmdstanr",mc.cores=4)
#options(digits=2, scipen=999, dplyr.summarise.inform=FALSE, kableExtra.auto_format=FALSE)
walk(c("brms","dplyr","bayestestR","here","rstanarm"), conflict_prefer_all, quiet = TRUE)
walk(c("Display_Functions","fun_alm","fun_indv_fit","fun_model", "prep_model_data","org_functions"), ~source(here::here(paste0("Functions/", .x, ".R"))))
#conflicts_prefer(tidybayes::rstudent_t)

@@

This project is based on the following publication:

Gorman, T. E., & Goldstone, R. L. (2022). An instance-based model account of the benefits of varied practice in visuomotor skill. *Cognitive Psychology*, 137, 101491.

@@

{{< include pre_sections/diss_cv.qmd >}}

### 2024-10-12 Manuscript/manuscript_full.qmd
cv additions and re-render
few new references, and a re-render with the intro figure.

---
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
toc: false
toc-depth: 4
toc-location: body
#cache: true
output-dir: output
execute: 
  warning: false
  include: true
  echo: false
format:
#   docx:
#     prefer-html: true
#     output-file: "TG_Full_Dissertation2.docx"
#     toc: true
#   html:
#     toc: true
#     language: 
#       title-block-published: "Latest version"
#     shift-heading-level-by: 0
#     toc-depth: 4
#     link-citations: true
#     page-layout: full
#     format-links: [pdf, gfm, docx]
#     theme: 
#        #- ../Assets/Style/lux-modified.scss 
#        - cosmo
#        - custom.scss
#        - ../Assets/Style/style.scss
#     css: ../Assets/Style/calloutTG.css
#     citeproc: false
#     filters: 
#       - "_extensions/wordcount/citeproc.lua"
#       - "_extensions/wordcount/wordcount.lua"
#     lightbox: auto
#     knitr:
#       opts_chunk:
#         dev: "ragg_png"
#         dpi: 300
  pdf:
    cite-method: citeproc
    #date: today
    output-file: "TG_Full_Dissertation2.pdf"
    mathfont: "Libertinus Math"
    documentclass: article
    papersize: letter
    fontsize: 11pt
    linestretch: 1.5
          # Document styling
    geometry:
      - top=1in     
      - bottom=1in  
      - left=1in    
      - right=1in  
      - heightrounded

@@

{{< include pre_sections/pre_pdf_full.qmd >}}

@@

::: {.content-visible when-format="docx"}
{{< include pre_sections/pre_docx.qmd >}}
:::

>>>>

---
code-repo: "Access the code, data, and analysis at <https://github.com/tegorman13/Dissertation>"
toc: false
toc-depth: 4
toc-location: body
#cache: true
output-dir: output
execute: 
  warning: false
  include: true
  echo: false
format:
  docx:
    prefer-html: true
    output-file: "TG_Full_Dissertation2.docx"
    toc: true
#   html:
#     toc: true
#     language: 
#       title-block-published: "Latest version"
#     shift-heading-level-by: 0
#     toc-depth: 4
#     link-citations: true
#     page-layout: full
#     format-links: [pdf, gfm, docx]
#     theme: 
#        #- ../Assets/Style/lux-modified.scss 
#        - cosmo
#        - custom.scss
#        - ../Assets/Style/style.scss
#     css: ../Assets/Style/calloutTG.css
#     citeproc: false
#     filters: 
#       - "_extensions/wordcount/citeproc.lua"
#       - "_extensions/wordcount/wordcount.lua"
#     lightbox: auto
#     knitr:
#       opts_chunk:
#         dev: "ragg_png"
#         dpi: 300
  pdf:
    cite-method: citeproc
    #date: today
    output-file: "TG_Full_Dissertation2.pdf"
    mathfont: "Libertinus Math"
    documentclass: article
    papersize: letter
    fontsize: 11pt
    linestretch: 1.5
          # Document styling
    geometry:
      - top=1in     
      - bottom=1in  
      - left=1in    
      - right=1in  
      - heightrounded

@@

{{< include pre_sections/pre_pdf_full.qmd >}}
{{< include pre_sections/acknowledgements.qmd >}}
{{< include pre_sections/abstract.qmd >}}

@@

::: {.content-visible when-format="docx"}
{{< include pre_sections/pre_docx.qmd >}}
{{< include pre_sections/acknowledgements.qmd >}}
{{< include pre_sections/abstract.qmd >}}
:::
{{< pagebreak >}}

### 2024-10-12 Manuscript/pre_sections/pre_docx_full.qmd
few new references, and a re-render with the intro figure.

>>>>

My dissertation would not have been possible without the support and guidance of numerous individuals who have shaped my academic and personal growth.

First, I am deeply grateful to my advisor, Rob Goldstone, for his nearly limitless patience, clear thinking, and unwavering guidance. His ability to effortlessly demonstrate the power of so many tools has been awe-inspiring, and I am forever thankful for his mentorship. I also extend my heartfelt thanks to Dr. Rob Nosofsky for his sharp questions and encouragement of model-based thinking, and to Dr. Peter Todd for being a constant source of encouragement.

My foundation in psychological science was laid at the University of Wisconsin-Madison. I am indebted to Dr. Shawn Green, who took a chance on me despite my mediocre grades and lack of experience, introducing me to the world of psychological research. Special thanks to Aaron Cochrane for answering my countless questions, introducing me to R, and advanced data analysis techniques.

I am grateful for the camaraderie and intellectual stimulation provided by my friends at Indiana University, particularly those in the Geolab and Psychology department. Johnathan Avery, Eleanor Schille-Hudson, Mahi Luthra, Dan Levitas, Sam Nordli, Brad Rogers, Marina Dubova, Eeshan Hasan, and many others have been integral to my graduate school experience. A special mention goes to Jack Avery for introducing me to rock climbing and engaging in fun conversations that often led to unexpected ideas.

The teachers at Pardeeville High School played an essential role in nurturing my curiosity and establishing the educational foundation that shaped my early learning. The professors at UW-Madison and Indiana University further cultivated that curiosity, profoundly influencing my academic development.

I would also like to extend my heartfelt thanks to my family. My parents, Mary and Jim Gorman, have always been a source of love and unwavering belief in my abilities. My brother, Joseph, played a pivotal role in helping me through the final stages of my dissertation by providing a supportive environment and the encouragement I needed. Their collective support has made this journey not only possible but meaningful, and I will always be deeply grateful for it.

### 2024-10-12 Manuscript/pre_sections/pre_pdf_full.qmd
few new references, and a re-render with the intro figure.

Submitted to the faculty of the University Graduate School \\
in partial fulfillment of the requirements \\
for the degree \\
Doctor of Philosophy \\
in the Cognitive Science Program and \\
Department of Psychological and Brain Sciences, \\
Indiana University \\
September 2024

@@

\newpage
\begin{center}
\textbf{Acknowledgements}
\end{center}
\newpage

>>>>

Submitted to the faculty of the University Graduate School \\
in partial fulfillment of the requirements \\
for the degree \\
Doctor of Philosophy \\
in the Cognitive Science Program and \\
Department of Psychological and Brain Sciences, \\
Indiana University \\
October 2024

@@

### 2024-10-12 Sections/Introduction.qmd
few new references, and a re-render with the intro figure.

One of the earliest and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978. Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task. The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet. Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial. 12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants. Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage. In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children. This result provides particularly strong evidence for the benefits of varied practice, as the varied group outperformed the constant group even when tested at the "home-turf" distance that the constant group had exclusively practiced. A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a]. One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group. Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths. However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperforms the constant group even from the constants group's home turf has not been consistently replicated. One recent study attempted a near replication of the Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet). This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups. However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).

>>>>

One of the earliest and still often cited investigations of Schmidt's benefits of variability hypothesis was the work of @kerrSpecificVariedPractice1978. Two groups of children, aged 8 and 12, were assigned to either constant or varied training of a bean bag throwing task. The constant group practiced throwing a bean-bag at a small target placed 3 feet in front of them, and the varied group practiced throwing from a distance of both 2 feet and 4 feet (see @fig-ex-design1). Participants were blindfolded and unable to see the target while making each throw but would receive feedback by looking at where the beanbag had landed in between each training trial. 12 weeks later, all of the children were given a final test from a distance of 3 feet which was novel for the varied participants and repeated for the constant participants. Participants were also blindfolded for testing and did not receive trial by trial feedback in this stage. In both age groups, participants performed significantly better in the varied condition than the constant condition, though the effect was larger for the younger, 8-year-old children. This result provides particularly strong evidence for the benefits of varied practice, as the varied group outperformed the constant group even when tested at the "home-turf" distance that the constant group had exclusively practiced. A similar pattern of results was observed in another study wherein varied participants trained with tennis, squash, badminton, and short-tennis rackets were compared against constant subjects trained with only a tennis racket [@greenPracticeVariabilityTransfer1995a]. One of the testing conditions had subjects repeat the use of the tennis racket, which had been used on all 128 training trials for the constant group, and only 32 training trials for the varied group. Nevertheless, the varied group outperformed the constant group when using the tennis racket at testing, and also performed better in conditions with several novel racket lengths. However, as is the case with many of the patterns commonly observed in the "benefits of variability" literature, the pattern wherein the varied group outperforms the constant group even from the constants group's home turf has not been consistently replicated. One recent study attempted a near replication of the  Kerr & Booth study [@willeyLongtermMotorLearning2018], having subjects throw beanbags at a target, with the varied group training from positions (5 and 9 feet) on either side of the constant group (7 feet). This study did not find a varied advantage from the constant training position, though the varied group did perform better at distances novel to both groups. However, this study diverged from the original in that the participants were adults; and the amount of training was much greater (20 sessions with 60 practice trials each, spread out over 5-7 weeks).
